\section{Population Selection \& Sample Statistics}
\subsection{Population Galaxy Properties}
\subsubsection{SDSS II DR7 MPA-JHU dAGN Sample}

Over the past decade, since the inception of the Sloan Digital Sky Survey (SDSS), the ability to study the host galaxies of AGN has vastly increased. An offshoot of the many numerous parent AGN samples [e.g., \cite{Zakamska2003}; \cite{Kewley_2006}; \cite{Stasinska_2006}; \cite{Wild_2010}] are the dual AGN candidate samples [\cite{Smith_2010}; \cite{Liu_2012}; \cite{Ge_Hu_Wang_Bai_Zhang_2012}; \cite{2012ApJ...753...42C}]. The Liu+2010 (see: \cite{Liu_2009}) Type 2 AGNs with double-peaked [OIII] lines sample forms the basis of our study, with double-peaked [O III] profile candidate dual AGN objects cross-referenced from (see: \cite{Ge_Hu_Wang_Bai_Zhang_2012}) and AGN pairs from \cite{Liu_2012}. Utilising these candidate samples coupled to our own analysis, we are attempting to better understand the star-formation properties and evolutionary phases of dual AGN relative to normal single-peaked AGN. 

Analysis conducted by \cite{Ge_Hu_Wang_Bai_Zhang_2012} of 927,552 galaxy spectra from the SDSS DR7 MPA-JHU5 DR7 galaxy spectra data release\footnote{\tiny{Max-Planck-Institut für Astrophysik/John Hopkins University Data Release 7 (MPA/JHU5 DR7) reference: \tt{http://www.mpa-garching.mpg.de/SDSS/DR7/}.}} SDSS-DR7 [\cite{2009ApJS..182..543A}] using the emission-line measurements of $\text{H}\alpha$, $\text{[O III]}$ and $\text{H}\beta$ found a total of 3030 double-peaked narrow-emission line galaxies (NELs) and 12,582 with asymmetric, top-ﬂat proﬁles with a $\text{S/N}$ ratios ${>}{9}$ and equivalent widths EW($\text{H}\alpha$, $\text{H}\beta$, or $\text{[O III]}$) ${>}{3}Å$. The nature of the emission-line profiles were then extracted with STARLIGHT\footnote{\tiny{The SEAGal/STARLIGHT spectral synthesis code: \tt{http://astro.ufsc.br/starlight/}}} with a combination of narrow Gaussian, broad Balmer and $\text{[O III]}$ winged fits. The selection methods for the Ge+2012 sample is outlined in detail in §2 of \cite{Ge_Hu_Wang_Bai_Zhang_2012}. The entirety of the Ge+2012 double-peaked and asymmetric NEL population sample can be found at: \tt{[http://vizier.cfa.harvard.edu/viz-bin/VizieR?-source=J/ApJS/201/31]}.

Whilst the \cite{Ge_Hu_Wang_Bai_Zhang_2012} sample is numerous in its extent, a number of objects still hold ambiguities in their classification (e.g., prescribed therein as 'Type 5') as well as a number of objects are also designated as Type 1, that is they are double-peaked broad-line Type I AGN and their dual nature was not confirmed conclusively. Conversely, the \cite{Liu_2012} sample of Type II (narrow-line) AGN and composite pairs provides us with an interesting cross-reference for the \cite{Ge_Hu_Wang_Bai_Zhang_2012} sample; providing our original Ge+2012 sample with confirmed AGN pairs with tidal classifications (i.e., 0 = non-interactions; 1 = ambiguous; 2 = tidal; 3 = 'dumbbell systems'), transverse proper separations, $\text{r}_{\text{p}}$ ($\text{h}_{70}^{-1}$ $\text{kpc}$), and angular separations, $\Delta\Theta$. 

From the original Liu+2011 sample of 2818, as stated above we focused our attention on Type II narrow-line AGN pairs (a total of 2532) and looked to cross-reference these objects with the full Ge+2012 sample (a total of 15612). From this cross-referencing we have a total of 99 objects which are designated as narrow-line Type II AGN or NL quasar (QSO) pairs by Lui+2011 (QSO pairs attributed to Reyes et al. 2008) and are also designated as either Type II + Type II, Type II + SF or ambiguous/unclassified by Ge+2012. This cross-correlation not only allows us to understand the emission profile and fluxes of the redshifted and blueshifted [O III] components, but also allows us to understand the interaction or merger-phase of the host AGN pairs. Ideally, the cross-comparative study will allow us to identify SFR for individual systems whilst simultaneously having an understanding of the transverse proper separation, $\text{r}_{\text{p}}$, and tidal features giving a more accurate picture of the SFR as related to the merger stage, i.e., close-interaction, distant-interaction, etc. Furthermore, we can fully utilise the flux measurements of these objects from DR10 from the SDSS as well as making further comparisons with local narrow-line AGN in the same redshift extent as our parent sample. The entirety of the Liu+2011 AGN pair population sample can be found at: \tt{[http://vizier.cfa.harvard.edu/viz-bin/VizieR?-source=J/ApJ/737/101]}.

The Ge+2012 sample contains a myriad of objects classified as binary objects, for example binary star-forming galaxies, binary Type II AGN and composite or mixed Type II AGN-star forming objects. Of the total initial Ge+2012 sample of 15611 objects, we target our analysis on 3841 objects designated as Ge+2012 Type 2 AGN by the emission-line analysis of the MPA-JHU DR7 ($\sim{0.4}$\% of the total MPA-JHU5 SDSS galaxy sample), i.e., objects which are confirmed binary Type II Seyferts within the low-redshift range (e.g., ${0.00824}<{z}<{0.37712}$; with galaxy velocity dispersions, $\sigma$ (km s$^{-1}$), ranging from 44.10 to 500). The motivations behind this choice coincides with the Ge+2012 catalogue containing a large number of prospective Seyfert Type II binary AGN as well as the prevalence of young stellar populations within the bulges of nearby Seyfert galaxies [e.g., \cite{1990MNRAS.242..271T}; \cite{Delgado_2001}] and a general global enhanced star-formation prevalence within Seyfert IIs [e.g., \cite{2006MNRAS.366..480G}].  

Within this smaller binary Type II sub-sample of dAGN candidates are other attached peculiarities and emission-line classifications. Associated to the emission-line features are the classifications of `pp', i.e., double-peaked narrow emission-line (NEL) objects, and `as', i.e., asymmetric top-flat NEL objects. Further to the emission-line classifications are the `2` and `A' peculiarities indicating galaxies with dual-cores and AGNs with strong $\text{[O III]}$ wings, respectively, with a peculiarity designation of A+2 representing objects which show both resolvable dual-cores in SDSS imaging as well as strong $\text{[O III]}$ wings. A full overview of the spectral emission-line features of the Ge+2012 can be found in §2.1, §2.2 and §2.3 of \cite{Ge_Hu_Wang_Bai_Zhang_2012}. Overall, we should combine the strengths of the two samples to give a much broader picture of the dual AGN star formation connection.

\subsubsection{SDSS II DR7 MPA-JHU Type II dual AGN Sample: Liu+2010}

In order to better understand the star-formation properties of dual AGN we started with a sample of 167 Type II dual AGN from \cite{Liu_2009}. The objects within this candidate dual AGN sample where selected on the following criteria: (1) the rest-frame wavelength ranges [4700, 5100]\AA{} and [4982, 5035]\AA{} centred on the $\text{[O III]}$ $\lambda$$5007$\AA{} line have median signal-to-noise ratio (S/N) > 5 pixel$^{−1}$ and bad pixel fraction <30\%; (2) the $\text{[O III]}$ $\lambda$$5007$\AA{} line is detected at >5$\sigma$ and has a rest-frame EW > 4\AA; (3) the line flux ratio $\text{[O III]}$ $\lambda$$5007$/$\text{H}\beta$ > 3 if ${z}<{0.33}$, or the diagnostic line ratios $\text{[O III]}$ $\lambda$$5007$/$\text{H}\beta$ and $\text{[N II]}$ $\lambda$$6584$/$\text{H}\alpha$ lie above the theoretical upper limits for star-formation excitation from \cite{Kewley_Dopita_Sutherland_Heisler_Trevena_2001} on the BPT emission-line diagnostic diagram [\cite{Baldwin_1981}] if ${z}<{0.33}$. From these constraints \cite{Liu_2009} selected a total of 167 objects which yielded unambiguous double-peaked $\text{[O III]}$ emission lines. The Liu+2010 candidate dual AGN sample has a redshift extent of ${0.0319}<{z}<{0.6427}$, hence some objects will have their $\text{[N II]}$ $\lambda$$6584$/$\text{H}\alpha$ complex excluded from the spectral observation. For our analysis we exclude those objects where their redshifts do not allow for the $\text{[N II]}$ $\lambda$$6584$/$\text{H}\alpha$ complex to be visible in the optical window. Importance is also placed on the distinguishability of the $\text{H}\beta$ emission profile as we place an importance on the Balmer decrement $\text{H}\alpha/\text{H}\beta$ of both our dual AGN sample and our local AGN control sample.

As outlined in \cite{Liu_2009}, the Type II candidate dual AGN sample shows systematically larger stellar velocity dispersions and masses, older mean stellar ages (and redder colours) and smaller fractions of post-starburst populations in the past $0.1–1$ Gyr compared to their AGN control sample. This somewhat contradicts the idea that dual AGN should host higher levels of star-formation than their single AGN counterparts if they are indeed a result of two merging galaxies. However, as discussed in \cite{Liu_2009}, and others, many dual AGN may be attributed to narrow-line region kinematics (such as rotating gaseous discs on kpc scales, asymmetrical jets or biconical outflows). Hence, within our parent candidate dual AGN sample there is a high certainty that not all double-peaked emission line objects are attributable to dual AGN; however, \cite{Liu_2009} state that the double-peaked objects are not exclusively attributed NLR kinematics due to a lack of ionisation stratification, with consistent velocity offsets in $\text{H}\beta$ and $\text{[O III]}$ also being measured.

\subsubsection{SDSS III DR10 Portsmouth Group dAGN Sample}

Further to the DR7 data we analyse the Ge+2012 sample in light of the latest SDSS data release (SDSS III DR10). We cross-reference the Ge+2012 Type 2 Seyfert pair sample with emission-line flux measurements and stellar kinematic measurements [see: \cite{Thomas_2013}] from the Galaxy Properties database from the Portsmouth Group\footnote{\tiny{Galaxy Properties from the Portsmouth Group: \tt{http://www.sdss3.org/dr10/spectro/galaxy_portsmouth.php#kinematics}}}$^{\text{,}}$\footnote{\tiny{Portsmouth stellar kinematics and emission-line flux measurements [Thomas et al. 2013] are based on adaptations of the publicly available codes Penalized PiXel Fitting (pPXF, [Cappellari \& Emsellem 2004]) and Gas and Absorption Line Fitting code (GANDALF v1.5; [Sarzi et al. 2006])}} for SDSS and BOSS galaxies. The Portsmouth Galaxy Group database utilises GANDALF (\textit{G}as \textit{and} \textit{A}bsorption \textit{L}ine \textit{F}itting code; [\cite{Sarzi_2006}]) and pPXF (\textit{P}enalized \textit{P}i\textit{X}el \textit{F}itting; [\cite{2012ascl.soft10002C}]). This new spectral fitting approach fits stellar population and Gaussian emission line templates to the galaxy spectrum simultaneously to separate stellar continuum and absorption lines from the ionized gas emission using GANDALF. Stellar kinematics are then evaluated by pPXF where the line-of-sight velocity distribution is fitted directly in pixel space. The fits account for the impact of diffuse dust in the galaxy on the spectral shape adopting a \cite{Calzetti_2001} obscuration curve. The code further determines the kinematics of the gas (velocity and velocity dispersion) and measures emission line fluxes and equivalent widths (EWs) on the resulting Gaussian emission line template.

From the initial SDSS DR7 MPA-JHU sample we find 3348 that can be cross-referenced with the \tt{emissionLinesPorts} database from SDSS III DR10 (a total of $\sim{87.16}$\% of the total Ge+2012 sample). This smaller sub-set has had BPT diagram re-classifications: 562 (i.e., $16.78$\%) Seyfert--2, with 2244 composite AGN-SF objects (i.e., $67.02$\%). The remaining are re-classified as either LINER or star-forming galaxies. Further to the designations from the \tt{emissionLinesPorts} DR10 database we analyse the redshifted and blueshifted components in light of the new SDSS III analyses.

\subsection{Control Sample}

\subsubsection{SDSS AGN Control Sample}

To constrain the AGN contribution to the $\text{[O II]}$ emission, we again utilised the vast spectroscopic database of the SDSS in the search for narrow-line Type II AGN. To confirm an object as a Type II AGN for this study we impose the following criteria: (1) the emission-line ratio $\log(\text{[O III]}/\text{H}\beta)>{0.690}$, with a preference for $\text{[O III]}$ $\lambda$5007/$\text{H}\beta$ > 10; (2) the flux profiles are best fitted with Gaussian components with velocity dispersions of 600 < FWHM (km s$^{-1}$) < 1000; (3) a S/N ratio > 8, with an ideal preference towards high S/N objects; (4) the maximum redshift is $\sim{0.3}$ to allow for the $\text{[N II]}$ $\lambda$6584/$\text{H}\alpha$ complex to not be excluded from the spectral observation. As with our dual AGN sample, importance is placed on on the Balmer decrement $\text{H}\alpha$/$\text{H}\beta$ measurement. In the cases where $\text{H}\beta$ is measurable, the width of the $\text{H}\beta$ component was fixed to the best-fit value of the $\text{[O II]}$ component. Focusing on SDSS Type II narrow-line AGN will allow much more accurate measurements of the SFR as the optical light, particularly the aforementioned $\text{[O II]}$ doublet and the $\text{H}\alpha$ emission-lines, is not strongly influenced by the activity of the SMBH nucleus in narrow-line AGN.
  
  
  
  
  