\section{Samples}
\subsection{Parent Sample}

\subsubsection{SDSS II DR7 MPA-JHU Type II dual AGN Sample: Liu+2010}

In order to better understand the star-formation properties of dual AGN we started with a sample of 167 Type II dual AGN from \cite{Liu_2009}. The objects within this candidate dual AGN sample where selected on the following criteria: (1) the rest-frame wavelength ranges [4700, 5100]\AA{} and [4982, 5035]\AA{} centred on the $\text{[O III]}$ $\lambda$$5007$\AA{} line have median signal-to-noise ratio (S/N) > 5 pixel$^{−1}$ and bad pixel fraction <30\%; (2) the $\text{[O III]}$ $\lambda$$5007$\AA{} line is detected at >5$\sigma$ and has a rest-frame EW > 4\AA; (3) the line flux ratio $\text{[O III]}$ $\lambda$$5007$/$\text{H}\beta$ > 3 if ${z}<{0.33}$, or the diagnostic line ratios $\text{[O III]}$ $\lambda$$5007$/$\text{H}\beta$ and $\text{[N II]}$ $\lambda$$6584$/$\text{H}\alpha$ lie above the theoretical upper limits for star-formation excitation from \cite{Kewley_Dopita_Sutherland_Heisler_Trevena_2001} on the BPT emission-line diagnostic diagram [\cite{Baldwin_1981}] if ${z}<{0.33}$. From these constraints \cite{Liu_2009} selected a total of 167 objects which yielded unambiguous double-peaked $\text{[O III]}$ emission lines. The Liu+2010 candidate dual AGN sample has a redshift extent of ${0.0319}<{z}<{0.6427}$, hence some objects will have their $\text{[N II]}$ $\lambda$$6584$/$\text{H}\alpha$ complex excluded from the spectral observation. For our analysis we exclude those objects where their redshifts do not allow for the $\text{[N II]}$ $\lambda$$6584$/$\text{H}\alpha$ complex to be visible in the optical window. Importance is also placed on the distinguishability of the $\text{H}\beta$ emission profile as we place an importance on the Balmer decrement $\text{H}\alpha/\text{H}\beta$ of both our dual AGN sample and our local AGN control sample.

As outlined in \cite{Liu_2009}, the Type II candidate dual AGN sample shows systematically larger stellar velocity dispersions and masses, older mean stellar ages (and redder colours) and smaller fractions of post-starburst populations in the past $0.1–1$ Gyr compared to their AGN control sample. This somewhat contradicts the idea that dual AGN should host higher levels of star-formation than their single AGN counterparts if they are indeed a result of two merging galaxies. However, as discussed in \cite{Liu_2009}, and others, many dual AGN may be attributed to narrow-line region kinematics (such as rotating gaseous discs on kpc scales, asymmetrical jets or biconical outflows). Hence, within our parent candidate dual AGN sample there is a high certainty that not all double-peaked emission line objects are attributable to dual AGN; however, \cite{Liu_2009} state that the double-peaked objects are not exclusively attributed NLR kinematics due to a lack of ionisation stratification, with consistent velocity offsets in $\text{H}\beta$ and $\text{[O III]}$ also being measured.

\subsection{Control Sample}

\subsubsection{SDSS AGN Control Sample}

To constrain the AGN contribution to the $\text{[O II]}$ emission, we again utilised the vast spectroscopic database of the SDSS in the search for narrow-line Type II AGN. To confirm an object as a Type II AGN for this study we impose the following criteria: (1) the emission-line ratio $\log(\text{[O III]}/\text{H}\beta)>{0.690}$, with a preference for $\text{[O III]}$ $\lambda$5007/$\text{H}\beta$ > 10; (2) the flux profiles are best fitted with Gaussian components with velocity dispersions of 600 < FWHM (km s$^{-1}$) < 1000; (3) a S/N ratio > 8, with an ideal preference towards high S/N objects; (4) the maximum redshift is $\sim{0.3}$ to allow for the $\text{[N II]}$ $\lambda$6584/$\text{H}\alpha$ complex to not be excluded from the spectral observation. As with our dual AGN sample, importance is placed on on the Balmer decrement $\text{H}\alpha$/$\text{H}\beta$ measurement. In the cases where $\text{H}\beta$ is measurable, the width of the $\text{H}\beta$ component was fixed to the best-fit value of the $\text{[O II]}$ component. Focusing on SDSS Type II narrow-line AGN will allow much more accurate measurements of the SFR as the optical light, particularly the aforementioned $\text{[O II]}$ doublet and the $\text{H}\alpha$ emission-lines, is not strongly influenced by the activity of the SMBH nucleus in narrow-line AGN.

\subsubsection{Sample Measurements: Optical SDSS Spectra}

Utilising the open access SDSS spectra of the Liu et al. (2010) sample targets, we performed measurements of the integrated flux (in units of $1\text{E}^{-17}$ erg s$^{-1}$ cm$^{-2}$) of the [O II] λ3726, λ3729 doublet as well as the double-peaked emissions from the Hβ, [O III] λ5007, Hα and [N II] λ6583 lines, host stellar velocity dispersion as well as the velocity offsets for the blue shifted and redshifted components to the Hβ and [O III] λ5007 emission-lines. We also obtained r band magnitudes for our sample from the SDSS MPA-JHU database. Measurements were obtained by utilising a well known gas and absorption line fitting code (\tt{GANDALF}; Sarzi et al. 2006) to fit a stellar continuum model to each spectrum. After subtracting the continuum models, we utilise the open access python based spectral fitting routine (pyspeckits; Ginsburg & Mirocha 2011) to fit two Voigt profiles to the double-peaked [O III] λ5007, Hβ, [O III] λ5007, Hα and [N II] λ6583 emission-lines with half widths of σ ~ 1.53 and 0.00 < γ < 1.00 to obtain the best goodness of fit parameter for each profile (i.e., a reduced χ2 statistic ~ 1). The [O II] λλ3726, 3729 Å doublet was treated separately to the ionisation ratio emission-lines, performing a normal Voigt fit centred on both the doublet theoretical peaks. Utilising the redshift values quoted by the SDSS we converted to the luminosity distance using the cosmological parameters quoted in §1.1 and we then converted the fluxes to luminosities accordingly to the method we prescribe for approximate corrections from the AGN contribution to the [O II] emission.